%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	\cventry{Founder \& Managing Director} % Job title
	{Fox and Duck Software Ltd.} % Organization
	{Norbury, Staffordshire, UK} % Location
	{Apr. 2015 — Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Delivering effective DevOps projects.}
		\item {Provides expertise in improving business processes with automation, continuous integration and deployment services, and mobile application development.}
		\end{cvitems}
	}

	\cventry{Senior DevOps Engineer}
	{Deloitte UK}
	{Birmingham, United Kingdom}
	{Nov. 2018 — Present}
	{
		\begin{cvitems}
			\item{Designed, developed and delivered SRE/DevOps solutions and provided guidance whilst embedded into development teams.}
			\item{Developed majority of Terraform code to deploy Javascript/Typescript Lambda functions and supporting infrastructure.}
			\item{Developed solution to provide useful metrics and alerts for monitoring using Prometheus, Cloudwatch, and Grafana.}
			\item{Built CICD Solution using Jenkins running on Kubernetes with dynamic slaves.}
			\item{Developed supporting Lambda functions in Python and Typescript.}
			\item{Assisted with development of ETL Solution written in Python.}
			\item{Technologies Used:}
				\begin{itemize}
					\item AWS
					\item Terraform
					\item Docker
					\item GitHub
					\item Kubernetes
					\item Prometheus
					\item Grafana
				\end{itemize}
		\end{cvitems}
	}

	\cventry{DevOps Engineer}
	{Oxford University Press}
	{Oxford, United Kingdom}
	{Aug. 2018 — Nov. 2018}
	{
		\begin{cvitems}
			\item{Designed, developed and delivered SRE/DevOps solutions and provided guidance whilst embedded into development teams.}
			\item{Provided support during deployments of infrastructure.}
			\item{Developed solutions to provide useful metrics and alerts for monitoring.}
			\item{Built demonstrations for Kubernetes, Prometheus and GitlabCI for key decision makers.}
			\item{Technologies Used:}
				\begin{itemize}
					\item AWS
					\item CloudFormation
					\item Azure
					\item ARM Templating
					\item Terraform
					\item Ansible
					\item Packer
					\item Docker
					\item GitHub
					\item Kubernetes
					\item Prometheus
					\item Gitlab
				\end{itemize}
		\end{cvitems}
	}
	
	\cventry{Site Reliability Engineer}
	{Capita / DWP}
	{Manchester, United Kingdom}
	{Apr. 2018 — Aug. 2018}
	{
		\begin{cvitems}
			\item{Designed, developed and delivered SRE/DevOps solutions and provided guidance to development teams.}
			\item{Provided support during deployments of infrastructure.}
			\item{Developed solutions to provide useful metrics and alerts for monitoring}
			\item{Developed a project to collate AWS Trusted Advisor reports into a single location.}
			\item{Technologies Used:}
				\begin{itemize}
					\item AWS
					\item Terraform
					\item Ansible
					\item Packer
					\item Docker
					\item GitLab
					\item GitLab CI
					\item Python
					\item Prometheus
				\end{itemize}
		\end{cvitems}
	}

	\cventry{Interim DevOps Engineer}
	{Kreditech SSL}
	{Remote / Hamburg, Germany}
	{Nov. 2017 — Mar. 2018}
	{
		\begin{cvitems}
			\item{Designed, developed, and delivered a robust Kubernetes solution allowing the underwriting team to deploy their code rapidly.}
			\item{Assisted and transferred knowledge of current DevOps and SRE technologies to other parts of the business.}
			\item{Technologies Used:}
				\begin{itemize}
					\item AWS
					\item Kubernetes
					\item Kubernetes Operations (kops)
					\item Terraform
					\item Ansible
					\item Packer
					\item Helm
					\item Docker
					\item Jenkins
					\item Scala
				\end{itemize}
		\end{cvitems}
	}

	\cventry{Senior Business Architecture Lead}
	{Lloyds Bank}
	{Central London, UK}
	{Jun. 2017 — Nov. 2017}
	{
		\begin{cvitems}
		\item {Developed, designed and supported the automated build and configuration of infrastructure across multiple cloud providers.}
		\item {Created multi-level designs for the orchestration system of the cloud providers.}
		\item {Developed, designed and supported a self-service system to orchestrate the deployment of architechure for application projects.}
		\item {Technologies Used: }
			\begin{itemize}
				\item {AWS}
				\item {Azure}
				\item {Google Cloud Platform}
				\item {Terraform}
				\item {Vault}
				\item {Chef}
				\item {Jenkins}
				\item {Red Hat Enterprise Linux}
				\item {JIRA \& Confluence}
				\item {Gitlab}
			\end{itemize}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry{DevOps Consultant} % Job title
	{EDF} % Organization
	{Brighton and Hove, UK} % Location
	{Apr. 2017 -- Jun. 2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Assisted with the Bluelab team with AWS and delivery with a mobile application with serverless backend technologies.}
		\item {Technologies Used: }
			\begin{itemize}
				\item {AWS}
					\begin{itemize}
						\item {CloudFormation}
						\item {Lambda}
						\item {Cognito}
						\item {SQS}
					\end{itemize}
				\item {Jenkins}
				\item {Red Hat Enterprise Linux}
			\end{itemize}
		\end{cvitems}
	}


    \cventry{DevOps Consultant (SC Cleared)} % Job title
    {Capgemini / Home Office} % Organization
    {Croydon, UK} % Location
    {Aug. 2016 — Apr. 2017} % Date(s)
    {
	    \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Developed and supported infrastructure using various technologies at the Home Office.}
	    \item {Involved in the Home Office Biometrics programme to deliver infrastructure code and support for use in the Biometrics Gateway (BSG) delivery project.}
	    \item {Encouraged best practises for Puppet development.}
	    \item {Technologies Used: }
		    \begin{itemize}
			    \item {Puppet}
			    \item {Vagrant \& VirtualBox}
			    \item {VMware ESX}
			    \item {Jenkins}
			    \item {Zabbix}
			    \item {Red Hat Enterprise Linux}
			    \item {JIRA, Stash (Bitbucket Server), \& Confluence}
			    \item {Node.js}
			    \item {Java}
			    \item {Maven}
			    \item {Openshift}
		    \end{itemize}
	    \end{cvitems}
    }


    \cventry{DevOps Tech Lead (SC Cleared)} % Job title
    {QA Consulting / HMRC} % Organization
    {Telford, UK} % Location
    {Apr. 2016 — Jun. 2016} % Date(s)
    {
	    \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Contracted in as an SME to develop a greenfield Puppet solution for handover to HMRC.}
	    \item {Using AWS EC2 machines Puppet was used to configure:}
		    \begin{itemize}
			    \item {A Gitlab community edition host.}
			    \item {Jenkins master and slave build servers.}
			    \item {Elasticsearch, Logstash and Kibana (ELK) Host.}
			    \item {Zabbix monitoring server and agents.}
			    \item {Nexus Repository Manager.}
			    \item {HMRC's main application stack: Pega \& Documentum.}
		    \end{itemize}
	    \item {I also assisted with the configuration of Gitlab and Nexus Repository Manager.}
	    \end{cvitems}
    }


  \cventry{Build Engineer (SC Cleared)} % Job title
	{Capita / Intellectual Property Office} % Organization
    {Newport, UK} % Location
    {Oct. 2015 — Mar. 2016} % Date(s)
    {
	    \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Contracted in as a SME in regards to Build/Release Engineering, DevOps processes, and to provide novel solutions to the issues that the current release team was experiencing at the Intellectual Property Office.}
	    \item {Involved with multiple projects the improve the speed and efficiency of the release team and strived to reduce workload.}
	    \item {Encouraged the use of the Git DVCS with Gitlab and the general use of open source software within the team.}
	    \item {Built a Release Management Tool with .Net Core in C\#, built in Docker containers for ease of deployment.}
	    \end{cvitems}
    }

    
  \cventry{Build Engineer} % Job title
    {Inspired Gaming Group} % Organization
    {Birmingham, UK} % Location
    {Oct. 2014 - Sep. 2015} % Date(s)
    {
	    \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Creating and supporting the Inspired Gaming Group build system using my skills in software engineering and GNU/Linux system administration and promoting DevOps methodology within the business.}
	    \item {Responsibilities included: Support and administration of GNU/Linux Servers, Created and developed novel solutions for the businesses automation needs}
	    \item{Worked with developers to improve their quality of life when working on new or existing games, Promote test driven development}
	    \item{Technologies and Tools used:}
		    \begin{itemize}
			    \item{Ubuntu GNU/Linux}
			    \item{Python}
			    \item{Flask Web Framework}
			    \item{Jenkins CI}
			    \item{Powershell and Bash}
			    \item{Groovy}
			    \item{SVN \& Git}
			    \item{HTML5 \& Javascript (JQuery)}
		    \end{itemize}
	    \end{cvitems}
    }

    
  \cventry{Application Support} % Job title
    {Police Mutual} % Organization
    {Lichfield, UK} % Location
    {Mar. 2013 — Oct. 2014} % Date(s)
    {
	    \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Supported a user facing C\#.NET application, providing bug-fixes and changes.}
	    \item {Created and actions data-fixes for aforementioned application within MSSQL.}
	    \item {Represented the IT department for contract negotiations and changes.}
	    \item {Technologies Used:}
		    \begin{itemize}
			    \item{Microsoft SQL (T-SQL)}
			    \item{C\#/Visual Basic}
			    \item{ASP.NET}
			    \item{Windows Forms \& WPF}
			    \item{IIS}
			    \item{SSIS/SSRS}
			    \item{System Centre Service Manager}
		    \end{itemize}
	    \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry{Support Analyst} % Job title
    {Compass Group} % Organization
    {Birmingham, UK} % Location
    {Sep. 2012 — Nov. 2012} % Date(s)
    {
	    \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Help end users solve issues they are currently having with PCs, POS devices and network devices to ensure they can continue working.}
	    \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry{Junior Developer} % Job title
    {Capgemini} % Organization
    {Birmingham, UK} % Location
    {Sep. 2011 — Aug. 2012} % Date(s)
    {
	    \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Developed in a small team a consolidated database/web front end to all personnel management within the company, using technologies such as ASP.NET, C\#, MSSQL, SSRS, SSIS.}
	    \item {Also developed and debugged a contract management system for the Department of Education within a medium sized team.}
	    \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
